### 2017-09-29 TF-vldb2018/sec-intro.tex

\revise{
\stab (1) We propose {\em team simulation}, a revision of traditional graph pattern matching, for top-$k$ team formation problem.
It extends existing methods by incorporating the structural and capacity constraints using pattern graphs (Section~\ref{sec-tsim}).
We formulate the dynamic top-$k$ team formation problem, to handle separate and simultaneous pattern and data updates,
in order to cope with the highly dynamic environment of team formation (Section~\ref{sec-tsim}).

}

>>>>

\stab (1) We propose {\em team simulation}, a revision of traditional graph pattern matching, for top-$k$ team formation (Section~\ref{sec-tsim}).
It extends existing methods by incorporating the structural and capacity constraints using pattern graphs .
To cope with the highly dynamic environment of team formation, we also formulate the dynamic top-$k$ team formation problem  (Section~\ref{sec-tsim}), for handling separate and simultaneous pattern and data updates.
